Investigating Toronto City Council Attendance

### 2024-09-21 paper/paper.qmd
wrote abstract & readme + uploaded initial sketches

---
title: "My title"
subtitle: "My subtitle if needed"
author: 
  - Wendy Yuan
date: "27 September 2024"
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

@@

cleaned_data <- read_csv(here::here("data/cleaned_data/cleaned_data.csv"))
```
\newpage

>>>>

---
title: "Investigating Toronto City Council Attendance"
subtitle: "Determining the Ideal Meeting Types and Months for the 2022-2026 Term"
author: 
  - Wendy Yuan
date: "27 September 2024"
date-format: long
abstract: "This paper looks at Toronto City Council attendance data and when meeting absences are highest and lowest. It specifically examines that evening meeting have greater absence rate compared to morning and afternoon. 2022 showed very little absences while 2023 showed many missed attendances. Additionally, March, May, July, and October have are greater proportion of absences - showing a pattern that every couple months has less attendance."
format: pdf
number-sections: true
bibliography: references.bib
---

@@

cleaned_data <- read_csv(here::here("data/cleaned_data/cleaned_data.csv"))
```
